Industrial Best Practice

### 2015-03-23 ibp/ibp.tex
finshd summary

\section{Summary, 1p}

The knowledge gained from the course has had both immediate and long term effects. Immediately, we were able to use the information regarding finding research topics, collaborating with industry and performing research. These topics were invaluable for us when it came to finding a research topic and company for our thesis. In regards to the long term value, information for working at a company or in a professional environment will undoubtedly be of use for us.

@@

\begin{itemize}
	\item Account of how you can use the knowledge from the course in your further work
\end{itemize}

>>>>

\section{Summary}
The knowledge gained from the course has had both immediate and long term benefits. Immediately, we were able to use the information regarding finding research topics, collaborating with industry and performing research. These topics were invaluable for us when it came to finding a research topic and company for our thesis. In regards to the long term value, information for working at a company or in a professional environment will undoubtedly be of use for us.

@@

The course has thought us how to apply the theoretical knowledge we have in a business setting. Other courses, such as pure programming courses, only teach you how to do something in theory but not how to use the skills in projects or at a company. This course in combination with the project courses will definitely help us in that.

Another more practical use of this course will be that it will help us to take a more structured and systematic approach in planning our career. Before we have only set goals that are quite loose and undefined, but now we can use real industry methods such as roadmaps to structure our career plan. This will definitely help us to choose a wiser path in our career and hopefully help us to find a job that suits us!
